Predicting the effects of character displacement on food-web dynamics

### 2019-02-08 manuscript_ECD_model.Rmd
implemented asymmetric models. I now identified follow-up scenarios that I have to explore (different pre-adaptations of single consumer)

## Linear
sim_2C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = LawlorSmith_2C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_linear, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))

@@

sim_1C_2R_LawlorSmith_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveDN, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveDN))
## concaveUP
sim_2C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_2C_2R, 
                                        eco_CR_model = LawlorSmith_2C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                        species_traits = c(1,2), 
                                        eco_param_names = c("a11","a22"), 
                                        eco_tradeoff_names = c("a12","a21"),  
                                        evo_param_names = c("a11m","a22m"),  
                                        evo_tradeoff_names = c("a12m","a21m"), 
                                        tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_1C_2R, 
                                        eco_CR_model = LawlorSmith_1C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith),
                                        species_traits = c(1), 
                                        eco_param_names = c("a11"), 
                                        eco_tradeoff_names = c("a12"),  
                                        evo_param_names = c("a11m"),  
                                        evo_tradeoff_names = c("a12m"), 
                                        tradeoff_functions = c(a12_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))

@@

## Linear
sim_2C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear, 
                                         init_states = states_2C_2R, 
                                         eco_CR_model = McCann_2C_2R, 
                                         AD_CR_models = c(mC1_McCann, mC2_McCann),
                                         species_traits = c(1,2), 
                                         eco_param_names = c("a11","a22"), 
                                         eco_tradeoff_names = c("a12","a21"),  
                                         evo_param_names = c("a11m","a22m"),  
                                         evo_tradeoff_names = c("a12m","a21m"), 
                                         tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_1C_2R_McCann_linear, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))

@@

sim_1C_2R_McCann_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_McCann_concaveDN, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_concaveDN))
## concaveUP
sim_2C_2R_McCann_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_McCann_concaveUP, 
                                          init_states = states_2C_2R, 
                                          eco_CR_model = McCann_2C_2R, 
                                          AD_CR_models = c(mC1_McCann, mC2_McCann),
                                          species_traits = c(1,2), 
                                          eco_param_names = c("a11","a22"), 
                                          eco_tradeoff_names = c("a12","a21"),  
                                          evo_param_names = c("a11m","a22m"),  
                                          evo_tradeoff_names = c("a12m","a21m"), 
                                          tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                          extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_McCann_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_McCann_concaveUP, 
                                          init_states = states_1C_2R, 
                                          eco_CR_model = McCann_1C_2R, 
                                          AD_CR_models = c(mC1_McCann),
                                          species_traits = c(1), 
                                          eco_param_names = c("a11"), 
                                          eco_tradeoff_names = c("a12"),  
                                          evo_param_names = c("a11m"),  
                                          evo_tradeoff_names = c("a12m"), 
                                          tradeoff_functions = c(a12_tradeoff),
                                          extra_tradeoff_params = c(A=A, n=n_concaveUP))
```

@@

## MacArthur asymmetry
#MacArthur_displacements_asymm <- mutate(sim_2C_2R_MacArthur_linear_asymm, Model = "MacArthur", n = n_linear, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_linear_asymm)), ]
#MacArthur_displacements_asymm$Time <- rep(c("Begin","End"),1)

MacArthur_displacements_asymm <- bind_rows(
  mutate(sim_2C_2R_MacArthur_linear_asymm, Model = "MacArthur", n = n_linear, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_linear_asymm)), ], 
  #mutate(sim_1C_2R_MacArthur_linear_asymm, Model = "MacArthur", n = n_linear, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_linear_asymm)), ],
  mutate(sim_2C_2R_MacArthur_concaveDN_asymm, Model = "MacArthur", n = n_concaveDN, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_concaveDN_asymm)), ], 
  #mutate(sim_1C_2R_MacArthur_concaveDN_asymm, Model = "MacArthur", n = n_concaveDN, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_concaveDN_asymm)), ],
  mutate(sim_2C_2R_MacArthur_concaveUP_asymm, Model = "MacArthur", n = n_concaveUP, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_concaveUP_asymm)), ])#, 
  #mutate(sim_1C_2R_MacArthur_concaveUP_asymm, Model = "MacArthur", n = n_concaveUP, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_concaveUP_asymm)), ]) 
MacArthur_displacements_asymm$Time <- rep(c("Begin","End"),3)

@@

@@

```

@@

<!--
Indeed, ecological character displacement often results in the evolution of characters that enhance a consumer’s ability to capture resources, which tends to destabilize consumer-resource interactions (Murdoch et al. 2003; McCann 2011). This occurs because increases in a consumer’s attack rate results in the resource being suppressed well below its carrying capacity, which if sufficient enough, can generate oscillations, and hence less stable, consumer-resource dynamics (Rosenzweig 1971; Murdoch et al. 2003). Experimental decreases in interaction strength between consumers and resources has been shown to promote coexistence between consumers and resources (Luckinbill 1973). Moreover, there is broad support that specialized consumers, since they are tightly coupled to their resources, tend to exhibit consumer-resource cycles, whereas this is not the case for generalists (Murdoch et al. 2002). Therefore, although evolutionary responses to exploitative competition may reduce the strength of interactions between consumers, they ultimately increase the strength of interactions with their resources which can destabilize the direct consumer-resource interaction (rather than the indirect consumer-consumer interaction). While prior models of character displacement have included more realistic functional responses and spatial relationships between consumers and resources, they have focused more on whether these factors alter patterns of character displacement rather than the effects of character displacement on the stability of the ecological community. As a consequence, it is currently unclear whether ecological character displacement has a net stabilizing or destabilizing effect on ecological communities.

@@

```{r MacArthur_Resources, include=FALSE, fig.cap="\\label{fig:MacArthur_Resources}Effect of character displacement on total attack rates (A) and resource densities (B) when consumers can forage for both resources simultaneously."}
Mac_attack <- ggplot(tradeoff_df, aes(x=aii/(aii+aij), y=aii+aij, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(MacArthur_displacements, Time=="End"), aes(x = a11/(a11+a12), y=a11+a12, fill=factor(n), shape=Competitor), size=3, color="black") + #, show.legend=FALSE) + size=5,
  #geom_point(data = filter(MacArthur_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=a11+a12, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  ylab(expression(a[ii]+a[ij])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21)) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

Mac_resources <- cbind.data.frame(select(tradeoff_df, n, aii, aij), MacArthur_2C_2R_tradeoff_dynamics) %>%
  ggplot(., aes(x=aii/(aii+aij), y=R1+R2, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(MacArthur_displacements, Time=="End"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=3, color="black") + #, show.legend=FALSE) + size=5,
  #geom_point(data = filter(MacArthur_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  ylab(expression(R[i]+R[j])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21)) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

@@

>>>>

## Linear
sim_2C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = LawlorSmith_2C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_linear, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_LawlorSmith_linear_asymm <- params_2C_2R_LawlorSmith_linear
params_2C_2R_LawlorSmith_linear_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_linear[nrow(sim_1C_2R_LawlorSmith_linear), c("a11","a12")] 
sim_2C_2R_LawlorSmith_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

@@

sim_1C_2R_LawlorSmith_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveDN, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveDN))
# asymmetric starting points
params_2C_2R_LawlorSmith_concaveDN_asymm <- params_2C_2R_LawlorSmith_concaveDN
params_2C_2R_LawlorSmith_concaveDN_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_concaveDN[nrow(sim_1C_2R_LawlorSmith_concaveDN), c("a11","a12")] 
sim_2C_2R_LawlorSmith_concaveDN_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveDN_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))

## concaveUP
sim_2C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_2C_2R, 
                                        eco_CR_model = LawlorSmith_2C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                        species_traits = c(1,2), 
                                        eco_param_names = c("a11","a22"), 
                                        eco_tradeoff_names = c("a12","a21"),  
                                        evo_param_names = c("a11m","a22m"),  
                                        evo_tradeoff_names = c("a12m","a21m"), 
                                        tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_1C_2R, 
                                        eco_CR_model = LawlorSmith_1C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith),
                                        species_traits = c(1), 
                                        eco_param_names = c("a11"), 
                                        eco_tradeoff_names = c("a12"),  
                                        evo_param_names = c("a11m"),  
                                        evo_tradeoff_names = c("a12m"), 
                                        tradeoff_functions = c(a12_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
# asymmetric starting points
params_2C_2R_LawlorSmith_concaveUP_asymm <- params_2C_2R_LawlorSmith_concaveUP
params_2C_2R_LawlorSmith_concaveUP_asymm[c("a21","a22")] <- sim_1C_2R_LawlorSmith_concaveUP[nrow(sim_1C_2R_LawlorSmith_concaveUP), c("a11","a12")] 
sim_2C_2R_LawlorSmith_concaveUP_asymm <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = LawlorSmith_2C_2R, 
                                AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveUP))

@@

## Linear
sim_2C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear, 
                                         init_states = states_2C_2R, 
                                         eco_CR_model = McCann_2C_2R, 
                                         AD_CR_models = c(mC1_McCann, mC2_McCann),
                                         species_traits = c(1,2), 
                                         eco_param_names = c("a11","a22"), 
                                         eco_tradeoff_names = c("a12","a21"),  
                                         evo_param_names = c("a11m","a22m"),  
                                         evo_tradeoff_names = c("a12m","a21m"), 
                                         tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_1C_2R_McCann_linear, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
# asymmetric starting points
params_2C_2R_McCann_linear_asymm <- params_2C_2R_McCann_linear
params_2C_2R_McCann_linear_asymm[c("a21","a22")] <- sim_1C_2R_McCann_linear[nrow(sim_1C_2R_McCann_linear), c("a11","a12")] 
sim_2C_2R_McCann_linear_asymm <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = McCann_2C_2R, 
                                AD_CR_models = c(mC1_McCann, mC2_McCann),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

# asymmetry with C1 starting with a different habitat preference (w)
params_1C_2R_McCann_linear_alt_w <- params_1C_2R_McCann_linear # NEED TO FIGURE OUT WHAT TO DO. i SHOULD PROBABLY MAKE SURE ATTACK RATES AND PREFERENCE ARE ALIGNED, BUT I SHOULD JUST DO THAT FOR THE ALTERNATIVE RESOURCE. E.G. C1 SPECIALIZING ON R2 INSTEAD OF R1 IN THE C1 ONLY SIMS.
sim_1C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_1C_2R_McCann_linear_alt_w, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))

@@

sim_1C_2R_McCann_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_McCann_concaveDN, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_concaveDN))
# asymmetric starting points
params_2C_2R_McCann_concaveDN_asymm <- params_2C_2R_McCann_concaveDN
params_2C_2R_McCann_concaveDN_asymm[c("a21","a22")] <- sim_1C_2R_McCann_concaveDN[nrow(sim_1C_2R_McCann_concaveDN), c("a11","a12")] 
sim_2C_2R_McCann_concaveDN_asymm <- eco_evo_CR(init_parameters = params_2C_2R_McCann_concaveDN_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = McCann_2C_2R, 
                                AD_CR_models = c(mC1_McCann, mC2_McCann),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))

## concaveUP
sim_2C_2R_McCann_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_McCann_concaveUP, 
                                          init_states = states_2C_2R, 
                                          eco_CR_model = McCann_2C_2R, 
                                          AD_CR_models = c(mC1_McCann, mC2_McCann),
                                          species_traits = c(1,2), 
                                          eco_param_names = c("a11","a22"), 
                                          eco_tradeoff_names = c("a12","a21"),  
                                          evo_param_names = c("a11m","a22m"),  
                                          evo_tradeoff_names = c("a12m","a21m"), 
                                          tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                          extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_McCann_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_McCann_concaveUP, 
                                          init_states = states_1C_2R, 
                                          eco_CR_model = McCann_1C_2R, 
                                          AD_CR_models = c(mC1_McCann),
                                          species_traits = c(1), 
                                          eco_param_names = c("a11"), 
                                          eco_tradeoff_names = c("a12"),  
                                          evo_param_names = c("a11m"),  
                                          evo_tradeoff_names = c("a12m"), 
                                          tradeoff_functions = c(a12_tradeoff),
                                          extra_tradeoff_params = c(A=A, n=n_concaveUP))
# asymmetric starting points
params_2C_2R_McCann_concaveUP_asymm <- params_2C_2R_McCann_concaveUP
params_2C_2R_McCann_concaveUP_asymm[c("a21","a22")] <- sim_1C_2R_McCann_concaveUP[nrow(sim_1C_2R_McCann_concaveUP), c("a11","a12")] 
sim_2C_2R_McCann_concaveUP_asymm <- eco_evo_CR(init_parameters = params_2C_2R_McCann_concaveUP_asymm,
                                init_states = states_2C_2R, 
                                eco_CR_model = McCann_2C_2R, 
                                AD_CR_models = c(mC1_McCann, mC2_McCann),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveUP))
```

@@

## MacArthur asymmetry. Note that all 1C_2R models are from the original simulations, as these were the starting points for the asymmetric sims (and therefore the appropriate comparison)
MacArthur_displacements_asymm <- bind_rows(
  mutate(sim_2C_2R_MacArthur_linear_asymm, Model = "MacArthur", n = n_linear, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_linear_asymm)), ], 
  mutate(sim_1C_2R_MacArthur_linear, Model = "MacArthur", n = n_linear, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_linear)), ],
  mutate(sim_2C_2R_MacArthur_concaveDN_asymm, Model = "MacArthur", n = n_concaveDN, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_concaveDN_asymm)), ], 
  mutate(sim_1C_2R_MacArthur_concaveDN, Model = "MacArthur", n = n_concaveDN, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_concaveDN)), ],
  mutate(sim_2C_2R_MacArthur_concaveUP_asymm, Model = "MacArthur", n = n_concaveUP, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_concaveUP_asymm)), ], 
  mutate(sim_1C_2R_MacArthur_concaveUP, Model = "MacArthur", n = n_concaveUP, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_concaveUP)), ]) 
MacArthur_displacements_asymm$Time <- rep(c("Begin","End"),6)

@@

# asymmetry
LawlorSmith_displacements_asymm <- bind_rows(
  mutate(sim_2C_2R_LawlorSmith_linear_asymm, Model = "LawlorSmith", n = n_linear, Competitor = "Yes")[c(1,nrow(sim_2C_2R_LawlorSmith_linear_asymm)), ], 
  mutate(sim_1C_2R_LawlorSmith_linear, Model = "LawlorSmith", n = n_linear, Competitor = "No")[c(1,nrow(sim_1C_2R_LawlorSmith_linear)), ],
  mutate(sim_2C_2R_LawlorSmith_concaveDN_asymm, Model = "LawlorSmith", n = n_concaveDN, Competitor = "Yes")[c(1,nrow(sim_2C_2R_LawlorSmith_concaveDN_asymm)), ], 
  mutate(sim_1C_2R_LawlorSmith_concaveDN, Model = "LawlorSmith", n = n_concaveDN, Competitor = "No")[c(1,nrow(sim_1C_2R_LawlorSmith_concaveDN)), ],
  mutate(sim_2C_2R_LawlorSmith_concaveUP_asymm, Model = "LawlorSmith", n = n_concaveUP, Competitor = "Yes")[c(1,nrow(sim_2C_2R_LawlorSmith_concaveUP_asymm)), ], 
  mutate(sim_1C_2R_LawlorSmith_concaveUP, Model = "LawlorSmith", n = n_concaveUP, Competitor = "No")[c(1,nrow(sim_1C_2R_LawlorSmith_concaveUP)), ]) 
LawlorSmith_displacements_asymm$Time <- rep(c("Begin","End"),6)

@@

# asymmetry
McCann_displacements_asymm <- bind_rows(
  mutate(sim_2C_2R_McCann_linear_asymm, Model = "McCann", n = n_linear, Competitor = "Yes")[c(1,nrow(sim_2C_2R_McCann_linear_asymm)), ], 
  mutate(sim_1C_2R_McCann_linear, Model = "McCann", n = n_linear, Competitor = "No")[c(1,nrow(sim_1C_2R_McCann_linear)), ],
  mutate(sim_2C_2R_McCann_concaveDN_asymm, Model = "McCann", n = n_concaveDN, Competitor = "Yes")[c(1,nrow(sim_2C_2R_McCann_concaveDN_asymm)), ], 
  mutate(sim_1C_2R_McCann_concaveDN, Model = "McCann", n = n_concaveDN, Competitor = "No")[c(1,nrow(sim_1C_2R_McCann_concaveDN)), ],
  mutate(sim_2C_2R_McCann_concaveUP_asymm, Model = "McCann", n = n_concaveUP, Competitor = "Yes")[c(1,nrow(sim_2C_2R_McCann_concaveUP_asymm)), ], 
  mutate(sim_1C_2R_McCann_concaveUP, Model = "McCann", n = n_concaveUP, Competitor = "No")[c(1,nrow(sim_1C_2R_McCann_concaveUP)), ]) 
McCann_displacements_asymm$Time <- rep(c("Begin","End"),6)

# write out data for exploring later and avoiding rerunning the simulations
write.csv(bind_rows(MacArthur_displacements, LawlorSmith_displacements, McCann_displacements), file = "symmetric_displacement_data.csv")
write.csv(bind_rows(MacArthur_displacements_asymm, LawlorSmith_displacements_asymm, McCann_displacements_asymm), file = "asymmetric_displacement_data.csv")
```

@@

<!--
Indeed, ecological character displacement often results in the evolution of characters that enhance a consumer’s ability to capture resources, which tends to destabilize consumer-resource interactions (Murdoch et al. 2003; McCann 2011). This occurs because increases in a consumer’s attack rate results in the resource being suppressed well below its carrying capacity, which if sufficient enough, can generate oscillations, and hence less stable, consumer-resource dynamics (Rosenzweig 1971; Murdoch et al. 2003). Experimental decreases in interaction strength between consumers and resources has been shown to promote coexistence between consumers and resources (Luckinbill 1973). Moreover, there is broad support that specialized consumers, since they are tightly coupled to their resources, tend to exhibit consumer-resource cycles, whereas this is not the case for generalists (Murdoch et al. 2002). Therefore, although evolutionary responses to exploitative competition may reduce the strength of interactions between consumers, they ultimately increase the strength of interactions with their resources which can destabilize the direct consumer-resource interaction (rather than the indirect consumer-consumer interaction). While prior models of character displacement have included more realistic functional responses and spatial relationships between consumers and resources, they have focused more on whether these factors alter patterns of character displacement rather than the effects of character displacement on the stability of the ecological community. As a consequence, it is currently unclear whether ecological character displacement has a net stabilizing or destabilizing effect on ecological communities.

@@

```{r MacArthur_Resources, include=FALSE, fig.cap="\\label{fig:MacArthur_Resources}Effect of character displacement on total attack rates (A) and resource densities (B) when consumers can forage for both resources simultaneously."}
Mac_attack <- ggplot(tradeoff_df, aes(x=aii/(aii+aij), y=aii+aij, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(MacArthur_displacements, Time=="End"), aes(x = a11/(a11+a12), y=a11+a12, fill=factor(n), shape=Competitor), size=3, color="white") + #, show.legend=FALSE) + size=5,
  geom_point(data = filter(MacArthur_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=a11+a12, fill=factor(n), shape=Competitor), size=1.5, color="white") +
  ylab(expression(a[ii]+a[ij])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21)) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

Mac_resources <- cbind.data.frame(select(tradeoff_df, n, aii, aij), MacArthur_2C_2R_tradeoff_dynamics) %>%
  ggplot(., aes(x=aii/(aii+aij), y=R1+R2, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(MacArthur_displacements, Time=="End"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=3, color="white") + #, show.legend=FALSE) + size=5,
  geom_point(data = filter(MacArthur_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=1.5, color="white") +
  ylab(expression(R[i]+R[j])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21)) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

@@

# Supplementary Material

```{r MacArthur_asymm, include=FALSE}
# replaced MacArthur_displacements with MacArthur_displacements_asymm
